---
title: "Optimization HW1"
author: "Alyson Brown"
date: "1/30/2019"
output:
  html_document: default
  pdf_document: default
---


*Note: I used ' to mean inverse throughout this homework...I couldn't figure out how to get a superscript of -1.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1

Let $B = A'$

So $B^T = (A')^T$

We know that $AB = I$

So then $(AB)^T = I^T$ and $A^TB^T = I$

From this equation we can say that $B^T = (A^T)'$

And so $B^T = (A')^T =(A^T)'$


## Q2

```{r Q2}

A = matrix(c(1, 1, 1, 1, .45, -.55, 0, 0, 0, 1, 0, 0, .14, .2, .2, .1), nrow = 4, ncol = 4, byrow = TRUE)
b =c(250000000,0,62500000,37500000)
A_inv = solve(A,b)
print(A_inv)


cat("Based on these parameters, the bank should lend $", A_inv[1], " in First Mortgage loans, $", A_inv[2], " in Second Mortgage loans, $", A_inv[3], " in Home Improvement loans, and $", A_inv[4], " in Personal Overdraft loans.")


```

## Q3

Let $x_1$ = number of units manufactured of product variant 1

Let $x_2$ = number of units manufactured of product variant 2

Let $x_3$ = number of units manufactured of product variant 3

Let $x_4$ = number of units manufactured of product variant 4


MAX Z = $1.5x_1 + 2.5x_2 + 3x_3 + 4.5x_4$

ST: 

  1) $2x_1 + 4x_2 + 3x_3 + 7x_4 <= 100,000$

  2) $3x_1 + 2x_2 + 3x_3 + 4x_4 <= 50,000$
    
  3) $2x_1 + 3x_2 + 2x_3 + 5x_4 <= 60,000$
    
  4) $x_1, x_2, x_3, x_4 >= 0$
    

## Q4
```{r Q4}

##Part A
#L = matrix(c(0,0,0,0, 0,0,0,0, 0,0,0,0, 0,0,0,0), nrow = 4, ncol = 4, byrow = TRUE)
L = matrix(0, nrow = 20, ncol = 20)

# Loop over my_matrix
for(row in 1:nrow(L)) {
  for(col in 1:ncol(L)) {
    if (col<row) {
      L[row, col] = col/row
    } else {
      L[row, col] = row/col
    }
    #print(L[row, col])
  }
}

print(L)


#Part B
tL <- t(L)
#print(tL)

if(all.equal(L, tL)){
  print('Yes it is symmetric!')
}

#Part C
C = solve(L)
#print(C)
all.equal((C%*%L),diag(1,20,20))

#Part D
d = c(1,2,3,4,5,6,7,8,9,10,10,9,8,7,6,5,4,3,2,1)

#Part E 
#Ax = Cd
#matrix multiplication A %*% B

```

* Note I use L here instead of A

Solve for x: $Lx = Cd$

We know that $C = L'$

$x = L'Cd$ and so $x = C*Cd$

```{r Q4E}

x = C%*%C%*%d
print(x)


```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
